Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples

### 2024-05-13 analyses/ewings-cell-type/03-copykat.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

## Validate common CNAs found in Ewing sarcoma

@@

`CopyKAT` outputs a matrix that contains the estimated copy numbers for each gene in each cell. 
We can read that in and look at the mean estimated copy numbers for each chromosome across each cell. 
We might expect that tumor cells would show an increased estimated copy number in Chr8, Chr12, and/or Chf 1 and a loss of Chr16.

>>>>

### Validate common CNAs found in Ewing sarcoma

@@

`CopyKAT` outputs a matrix that contains the estimated copy numbers for each gene in each cell. 
We can read that in and look at the mean estimated copy numbers for each chromosome across each cell. 
We might expect that tumor cells would show an increased estimated copy number in Chr8, Chr12, and/or Chr 1 and a loss of Chr16.
